Is it time for an NBA expansion?

### 2024-04-15 paper/paper.qmd
Model Update

# Fit a multiple linear regression model
nba_model <- lm(PTS ~ Year * Num_teams + AST + TRB + STL + BLK + TOV, data = sim_nba_data)
madal <- lm(PTS ~ Year + Num_teams + AST + TRB + STL + BLK + TOV, data = sim_nba_data)

>>>>

sim_nba_data <- sim_nba_data %>%
  mutate(
    PPG = PTS + 
          Year * 0.05 -           # Hypothetical influence of year on PPG
          Num_teams * 0.1 +       # Hypothetical influence of number of teams on PPG
          AST * 0.3 +             # Influence of assists per game
          TRB * 0.2 -             # Influence of rebounds per game
          STL * 0.15 +            # Influence of steals per game
          BLK * 0.1 -             # Influence of blocks per game
          TOV * (-0.25)           # Influence of turnovers per game
  )

# Fit a multiple linear regression model
nba_model <- lm(PTS ~ Year * Num_teams + AST + TRB + STL + BLK + TOV, data = sim_nba_data)
madal <- lm(PTS ~ Num_teams + AST + TRB + STL + BLK + TOV, data = sim_nba_data)
